\documentclass[11pt,a4paper,english,oneside,parskip=false]{scrartcl} %parskip=half
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

%\usepackage[a4paper, top=24mm, bottom=24mm, left=24mm, right=24mm]{geometry}

\usepackage{mathpazo}

\usepackage{hyphenat}
\usepackage{url}
\usepackage{hyperref}
\hypersetup{%
	final=true,%
	colorlinks=true,%
	linkcolor=black,%
	citecolor=black,%
	urlcolor=black,%
}
\usepackage[babel=true]{csquotes}
\usepackage{graphicx}

%\usepackage{todonotes}

\linespread{1.05}
\setkomafont{disposition}{\rmfamily}
\clubpenalty = 20000
\widowpenalty = 20000

\addto\extrasenglish{%
	\renewcommand{\sectionautorefname}{Section}
	\renewcommand{\subsectionautorefname}{Section}
	\renewcommand{\subsubsectionautorefname}{Section}
}


\begin{document}

\title{Bare\hyp{}Metal Installation of OceanTEA on Microsoft Windows}
%\author{Arne Johanson}
\date{}

\maketitle

\section{Overview}

Before installing OceanTEA itself, you need to install software that is required to run OceanTEA: 
\begin{enumerate}
	\item Git (version control system; \autoref{sec:git})
	\item NodeJS (JavaScript runtime environment; \autoref{sec:node})
	\item Anaconda (Python 3 distribution; \autoref{sec:anaconda})
\end{enumerate}
After having installed these dependencies, you will install OceanTEA as described in \autoref{sec:oceantea}. 



\section{Installing Git} \label{sec:git}

\begin{enumerate}
	\item Download the latest version of Git for Windows from:\\ \url{https://git-scm.com/download/win}
	\item Execute the setup program to install Git with default settings. 
\end{enumerate}



\section{Installing Node.js} \label{sec:node}

\begin{enumerate}
	\item Download the latest version of Node.js for Windows from:\\
	\url{https://nodejs.org/en/download/current/}
	\item Execute the setup program to install Node.js with default settings. 
\end{enumerate}



\section{Installing Anaconda} \label{sec:anaconda}

\begin{enumerate}
	\item Download the latest version of Anaconda \textbf{with Python~3} for Windows from:\\
	\url{https://www.continuum.io/downloads#_windows}\\
	Make sure to download the version that comes with Python~3 and \emph{not} with Python~2!
	\item Execute the setup program to install Anaconda with default settings. 
\end{enumerate}




\section{Installing OceanTEA} \label{sec:oceantea}

\begin{enumerate}
	\item Download the ZIP archive \texttt{oceantea\_bm.zip} from:\\
	\url{https://github.com/a-johanson/oceantea/raw/master/install/bare-metal/windows/oceantea_bm.zip}
	\item Extract the archive to any folder you have write access to (e.g., your Desktop).
	\item Navigate to the extracted files in the Explorer and execute \texttt{install\_oceantea\_bm.bat} by double\hyp{}clicking it.
	\item Wait for the installation process to complete. After it finishes, your default web drowser should open displaying the OceanTEA user interface. 
	To start or stop OceanTEA, execute \texttt{start\_oceantea\_bm.bat} or \texttt{stop\_oceantea\_bm.bat}, respectively.
\end{enumerate}


\end{document}
